Check links on old pages

### 2024-06-27 src/audit-cross-links.Rmd
Added nice-layout

load(file="../data/check_new.RData")
load(file="../data/check_old.RData")
```

### create subsets

```{r create}
md %>% 
  filter(miss==0) %>%
  select(yr, fn, stat, base) -> md1

html %>% 
  filter(miss==0) %>%
  mutate(base=fn) %>%
  mutate(html_yr=yr) %>%
  select(base, html_yr) -> html1

match1 <- full_join(md1, html1, by="base")

md %>% 
  filter(miss==0) %>%
  mutate(base=fn) %>%
  mutate(md_yr=yr) %>%
  select(base, md_yr) -> md2

html %>% 
  filter(miss==0) %>%
  mutate(base=link) %>%
  select(fn, yr, base) -> html2

match2 <- full_join(html2, md2, by="base")

```

### mistmatch 1a, new pages that link to non-existent old pages

```{r}
match1 %>% 
  filter(is.na(html_yr))
```

### mistmatch 1b, old pages that link back without recognition

```{r}
match1 %>% 
  filter(is.na(fn))
```

### mistmatch 2a, old pages that link to non-existent new pages

```{r}
match2 %>% 
  filter(is.na(md_yr))
```

### mistmatch 2b, new pages that link back without recognition

```{r}
match2 %>% 
  filter(is.na(fn))
```

>>>>

load(file="../data/check_new.RData")
n_new <- nrow(md)
load(file="../data/check_old.RData")
n_old <- nrow(html)
size_limit <- 99

inc <- function(x) {
  n <- length(x)
  m <- c(FALSE, x[-1]==x[-n])
  x[m] <- " "
  x
}
test1 <- rep(letters[1:4], 1:4)
test2 <- inc(test1)
data.frame(test1, test2)
```

### pages with no links from new site to old or blog site

```{r no-link-www}
md %>% 
  filter(miss==1) %>%
  select(yr, fn, stat) -> pip1 
print(nrow(pip1))
glue("{nrow(pip1)} / {n_new} = {round(100*nrow(pip1)/n_new)}%")
pip1 %>%
  mutate(yr=inc(yr)) %>%
  head(size_limit)
```

### pages with bad links from new site to old site

```{r bad-link-www}
html %>%
  rename(base=fn) %>%
  rename(subd=yr) %>%
  select(base, subd, stub) -> html1
md %>% 
  filter(miss==0) %>%
  filter(site=="www") %>%
  left_join(html1, by=c("subd", "base")) %>%
  select(yr, fn, stat, subd, base, stub) -> pip1
pip1 %>%
  filter(is.na(stub)) %>%
    select(-stub) -> pip2 
glue("{nrow(pip2)} / {n_new} = {round(100*nrow(pip2)/n_new)}%")
pip2 %>%
  mutate(yr=inc(yr)) %>%
  head(size_limit)
```

### pages with good links from new site to old site

```{r good-link-www}
pip1 %>%
  filter(!is.na(stub))  -> pip3 
glue("{nrow(pip3)} / {n_new} = {round(100*nrow(pip3)/n_new)}%")
pip3 %>%
  mutate(yr=inc(yr)) %>%
  head(size_limit)
```

### pages with no links from old site to new site

```{r no-link-new}
html %>% 
  filter(miss==1) %>%
  select(yr, fn, stub) -> pip1 
print(nrow(pip1))
pip1 %>%
  mutate(yr=inc(yr)) %>%
  head(size_limit)
```

### pages with bad links from old site to new site

```{r bad-link-new}
md %>%
  select(-link) %>%
  rename(link=fn) %>%
  select(link, stat) -> md1

html %>%
  filter(miss==0) %>%
  left_join(md1, by="link") %>%
  select(yr, fn, link, stat) -> pip1
pip1 %>%
  filter(is.na(stat)) %>%
  select(-stat)  -> pip4 
print(nrow(pip4))
pip4 %>%
  mutate(yr=inc(yr)) %>%
  head(size_limit)
```

### pages with good links from old site to new site

```{r good-link-new}
pip1 %>%
  filter(!is.na(stat)) -> pip5 
print(nrow(pip5))
pip5 %>%
  mutate(yr=inc(yr)) %>%
  head(size_limit)
```

### 2024-06-27 src/audit-old-pages.Rmd
Added nice-layout

```{r links}
search_link <- function(tx) {
  prefix1 <- '<p>This page is moving to a <a href="'
  prefix2 <- '<p>This page has moved to a <a href="'
  postfix <- '">new website</a>.</p>'
  prepost <- paste(prefix1, prefix2, postfix, sep="|")
  website <- "http://new.pmean.com/"
  slash   <- "/"
  tx %>%
    str_subset(prepost) %>%
    str_replace(prefix1, "") %>%
    str_replace(prefix2, "") %>%
    str_replace(postfix, "") %>%
    str_replace(website, "") %>%
    str_replace(slash,   "") %>%
    paste0("") -> piper
  piper %>%
    paste0(collapse=", ")
}
```

@@

```{r read}
full_name <-
  paste0(
  html_path, "/",
  html$yr, "/",
  html$fn, ".",
  html$ext)
html$size <- -1
html$link <- "999"
for (i in 1:n) {
  tx <- read_lines(full_name[i])
  html$link[i] <- search_link(tx)
  html$size[i] <- search_size(tx)
}
html$miss <- as.numeric(nchar(html$link) == 0)
html$stub <- as.numeric(html$size <= 10)
save(html, file=save_file)
```

>>>>

```{r links}
search_link <- function(tx) {
  prefix1 <- '<p>This page is moving to a <a href="'
  prefix2 <- '<p>This page has moved to a <a href="'
  postfix <- '">new website</a>.</p>'
  prepost <- paste(prefix1, prefix2, postfix, sep="|")
  website <- "http://new.pmean.com/"
  slash   <- "/"
  tx %>%
    str_subset(postfix) %>%
    str_replace(prefix1, "") %>%
    str_replace(prefix2, "") %>%
    str_replace(postfix, "") %>%
    str_replace(website, "") %>%
    str_replace(slash,   "") %>%
    str_remove_all("\\s") %>%
    str_trim %>%
    paste0("") -> piper
  piper %>%
    paste0(collapse=", ")
}
```

@@

```{r read}
# The str_trim function is not working. There
#  may be an encoding problem. See
#   "about_encoding" in the stringi package
#   https://search.r-project.org/CRAN/refmans/
#     stringi/html/about_encoding.html
#
# Help may come from the "stri_enc_toutf8" function 
#   https://search.r-project.org/CRAN/refmans/
#     stringi/html/stri_enc_toutf8.html
# A simpler solution may be
#   str_remove_all("\\s")
full_name <-
  paste0(
  html_path, "/",
  html$yr, "/",
  html$fn, ".",
  html$ext)
html$size <- -1
html$link <- "999"
for (i in 1:n) {
  tx <- read_lines(full_name[i])
  html$link[i] <- search_link(tx)
  html$size[i] <- search_size(tx)
}
html$miss <- as.numeric(nchar(html$link) == 0)
html$stub <- as.numeric(html$size <= 10)
html <- arrange(html, yr, fn)
save(html, file=save_file)
```
